Music Perception 2020: Stimuli profiles (random)

### 2020-10-12 material/stimuli/R/analysis/random.Rmd
random filtering
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../filtered/art_teaching", pattern = "txt")
lf_a_p <- list.files("../filtered/art_performing", pattern = "txt")
lf_d_t <- list.files("../filtered/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../filtered/dyn_performing", pattern = "txt")

>>>>

```{r file, include = FALSE}
# create a list of data file names
lf_a_t <- list.files("../random/art_teaching", pattern = "txt")
lf_a_p <- list.files("../random/art_performing", pattern = "txt")
lf_d_t <- list.files("../random/dyn_teaching", pattern = "txt")
lf_d_p <- list.files("../random/dyn_performing", pattern = "txt")
